Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-10-21 WSSSPE3/report/WSSSPE3_review.tex
small edits in keynote text

>>>>

WSSSPE3 began with a keynote speech delivered by Professor Matthew
Turk from the Department of Astronomy, University of Illinois titled \emph{Why
Sustain Scientific Software?}. Turk is a prolific practitioner of scientific
software and has extensive experiences working on large collaborative projects
employing modern computing tools. He is also a co-organizer and champion of all
the WSSSPE events so far.
